\section{Conclusion}\label{sec:conclusion}

At first, the recently into PROPOSAL implemented stochastic deflection is 
used to study the muon deflection per interaction. Mainly, the deflection 
is dominated by multiple scattering except for a few stochastic 
outliers by bremsstrahlung. These angles are lower $\sim\SI{1}{\degree}$. 

The results of PROPOSAL are tested against the common tools MUSIC and 
GEANT4 and all are in good agreement.
The median accumulated deflection depends on the final muon energy, primarily. 
This final energy can be interpreted as the muon energy at detector entry 
in neutrino telescopes. 
The outcome is fit by a polynom and can be used for 
a theoretical estimation of the muon deflection in water and ice.
This deflection defines a lower limit on the directional resolution.
At energies of $\SI{100}{\giga\electronvolt}$, there is a small impact of the muon deflection on the angular 
resolution of KM3NeT.

\textcolor{red}{relevance of muon-neutrino angle vs. muon deflection for higher energies}

\textcolor{red}{die finale energy des muons kann man so deuten, dass dies die energie ist, mit welcher das myon den detektor betritt -- somit gibt der plot die myonablenkung vor dem detektor an! -}
% \begin{itemize}
%     \item deflection per interaction is negligible
%     \item accumulated deflection is in the order of magnitude of KM3NeT for low energy muons (GeV-TeV) 
%     \item median accumulated defl can be fit and used for simple deflection estimation, since deflection mainly depends on final particle energy
%     \item relevance of muon-neutrino angle vs. muon deflection for higher energies
% \end{itemize}